Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-05-06 Ben_Manuscripts/transport/Draft.tex
Fixes in response to comments

  The uniform size and complex chemical topology of the pores that 
  constitute cross-linked inverted hexagonal (H\textsubscript{II})
  phase lyotropic liquid crystal (LLC) membranes make them promising
  for selective separations. In this work, we observe transport
  of water, sodium ions and 20 small polar solutes within the pores 
  of an LLC membrane using atomistic molecular simulations. We 
  find that the transport of a species is dependent not only on 
  molecular size, but on chemical functionality as well. The 
  membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. 
  %MRS3: remove qualifier?
  %In general, 
  We 
  %MRS3: tense
  %observed 
  observe
  that all solutes perform intermittent hops between lengthy
  periods of entrapment. Three different trapping mechanisms are 
  responsible for this behavior. First, solutes that drift
  out of the pore can become entangled among the dense monomer
  tails. Second, solutes can donate hydrogen bonds to the monomer
  head groups. Third, solutes can coordinate with sodium counter ions.
  The degree to which a solute is affected by each mechanism is 
  dependent on the chemical functionality of the solute. Using the
  insights developed in this study, we can begin to think about 
  how to redesign existing LLC membranes in order to perform 
  solute-specific separations.

@@

  All of these separations are possible in part with current commercial
  membrane separation techniques, but
  %MRS3: tweaking
  all still
  suffer from serious drawbacks. Currently,
  reverse osmosis (RO) and nanofiltration (NF) dominate commercial membrane
  separations of small molecules.~\cite{warsinger_review_2018} RO membranes are
  typically dense polymer matrices that separate solutes based on differences in
  their solubility and permeability in the membrane
  material.~\cite{fritzmann_state---art_2007} Although they can perform highly
  selective separations, high feed pressures and thus large amounts of energy
  are necessary in order to generate a useful permeate
  flux.~\cite{van_der_bruggen_review_2003} NF membranes have well-defined
  nm-sized pores which can give the same permeate flux as RO with lower applied
  pressure.~\cite{hilal_comprehensive_2004} However, the pores are not uniform in
  size, limiting their selectivity.~\cite{werber_materials_2016}.
%  Therefore, multiple membrane passes may be necessary in order to achieve 
%  high selectivity.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ortho_view.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{top_view.pdf}
  \caption{}
  \end{subfigure}
  %MRS3: include a bit more description in the caption of what the system: This is the figure that provides the orientation to the readers of what they will be thinking about for the rest of the paper.
  \caption{In both figures, water molecules that occupy the pores are colored blue,
  the hydrophilic head groups of the LLC monomers are colored orange with all else
  colored gray. 
  %MRS3: probably this point below can be better addressed in the text; looks a little out of place here.
  We expect that transport will be primarily determined by solute
  behavior within the pores. 
  (a) Membrane pores are approximately straight and (b)
  are packed hexagonally.}\label{fig:membrane_rendering}
  \end{figure}

  %MRS3: maybe say ``we present studies of''? ``This work'' is the paper, so using past tense is weird.
  In this work, we have studied the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of
  the membrane in which we placed solutes. We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
  Note that, in order limit our studies to uncharged species, we have only studied
  %BJC: citations for pKa's
  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
  pKa of acetic acid is 4.75.~\cite{chuysinuan_gallic_2009,perrin_pka_1981} 
  Assuming that the pKa of gallic acid is similar to NaGA3C11, it is possible
  for our sodium salted monomer to exist at the same time as protonated acetic
  acid. In any case, we are more interested in mechanisms of interaction with
  specific chemical functionality more than the behavior of specific molecules.

  \begin{table}[h!]
  \centering
%  \begin{minipage}{.4\textwidth}
%  \tiny
%  \begin{tabular}{ |lcc|lcc| }
  \begin{tabular}{ |m{3.5cm}m{1.4cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
    \hline
    \multicolumn{2}{|c}{Solute Name~~~~~~~~~Abbreviation} & Structure &\multicolumn{2}{c}{Solute Name~~~~~~~~~Abbreviation} & Structure \\
    \hline
	\color{blue}{\textbf{methanol}} & \color{blue}{\textbf{MeOH}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/MET.pdf}
    \end{minipage} &

@@

    \hline
  \end{tabular}
%  \end{minipage}
  \caption{Names of solutes along with their molecular structures and the
  abbreviations which we use in this paper. Colors correspond to solute groupings
  and are used in many plots. 
%  Blue corresponds to simple alcohols, red to 
%  diols, triols and sugars, green to ketone-like solutes, orange to sulfur-containing
%  solutes and yellow to solutes that can only accept hydrogen bonds but not donate.
  }\label{table:abbreviations}
  \end{table}

  %MRS2: generally, use present tense for what is being done in the paper, not future tense; 
  %the paper is completely written, later sections are not being written in the future. 
  %MRS2: descriptions of experiments can be in the past.   
  %MRS2: look over this section at the end of the intro again for clarity - some paragraphs are too short (ideas introduced and brushed past quickly) sometimes without strong theses.
  We first address the structure of the pores formed in the membrane.
  Previously, we have studied dry membrane systems and some systems with 
  low water content. We therefore first analyze how the radial density of monomer 
  components and water change within the pore based on membrane water content.

  We then present our efforts to understand how water partitions within the pores.
  From a macroscopic perspective, it might make sense to hypothesize that water 
  spends its time exclusively in the tube-like hydrophilic pore region. Our
  previous work showed that there is a gradual compositional transition from
  the hydrophilic to the hydrophobic region which means that solutes may not
  necessarily stay confined to the centers of the pores or even within the 
  pore region. 
  %MRS2: ``this information'' is ambiguous. Which information? Also, I'm not sure the paragraph above is enough to 
  %demonstrate why we can/should neglect the tails.
  We use this information in order to justify our restriction
  of solute transport studies to just the pore region.

@@

  In the remainder of the paper, we present our observations 
  and explanations of the observed transport mechanisms exhibited by water
  and solutes. 
  %MRS2: The thesis of this paragraph could be stronger. expand ``pores will restrict motion of the solutes'' a little using the physical details about the pores; paint the picture that will be filled in with detail   
Given that the pores will restrict motion of the solutes, we
  anticipate that transport will be hindered in some way.

  %MRS2: be consistent on tense.  What is presented in the paper is present tense.  We already studied it, we are presenting it.  
  We investigate the differences in solute motion, specifically its mean 
  squared displacement (MSD), based on a solute's size and chemical
  functionality. We will study the interactions between solutes, the membrane,
  and water in order to determine which mechanism or mechanisms dominate.

  There are also 
  %a couple of questions that are beyond
  several questions beyond
  the scope of this study.
  First, we will not study the concentration dependence of the observed transport
  rates. Although the average MSD might change with concentration, we are 
  focused on the underlying solute-membrane interactions that lead to the 
  observed transport mechanisms which we conjecture will remain roughly
  the same regardless of concentration. Second, we will not study the chemical potential
  of solutes in the pores, which could give us a better understanding of 
  equilibrium solute partitioning. However, this information is 
  %MRS3: added - there might be mechanisms that only happen with multiple solutes in contact
  likely
  not needed
  to understand the 
  %MRS3: added
  principal
  mechanistic details in various membrane regions. 
  %MRS3: broke sentence
  This work 
  %MRS3: added for flow
  instead
  represents a starting point for observing the types of interactions
  that occur between isolated solutes and the membrane.

@@

  Python scripts used to set up systems and conduct post-simulation trajectory 
  analysis 
  %MRS2: added to make sure it's clear the basic description is not JUST in the scripts.
  (as described below and in the supporting information) are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. 
  %BJC: also link to readthedocs? I have the link in the repo 
  %MRS2: either is fine. 
  The appropriate scripts to use for the subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supporting Information.
  We ran all molecular dynamics simulations and energy minimizations using GROMACS 2018.3 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}

@@

  We observed that some water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
  Information). We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent;
  %MRS3: providing some context
  otherwise, water would slowly leak from the pore into the tail region over several hundred nanoseconds.
We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region.
  %MRS2: seems like here is where we need to provide the justification for this decision, since the decision is described here (or, explain how we will justify it later)

@@

  The $z$-direction MSD of water in the 10 wt\% system \textit{is} linear
  %MRS2: added
  to within statistical precision.
  Therefore, for
  the purpose of comparison, we calculated its diffusion constant by fitting a line
  to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured particle displacement in one dimension.

@@

  In order to measure the length of hops, we first needed to detect
  when they occurred. We used an off-line change point detection 
  algorithm, implemented in the python package \texttt{ruptures}
  \cite{truong_ruptures:_2018}, in order to determine at which 
  points hops occurred in the time series of each solutes' COM. We
  used the 3 dimensional COM positions of each solute, rather than
  just the $z$-direction, in order to detect lateral hops. However,
  hop lengths are reported as their displacement in the $z$-direction.
  We reported the standard error in the average hop lengths by 
  bootstrapping the empirical distribution of observed
  hop lengths.\cite{efron_introduction_1994}
  % BJC: could add more detail about which algorithm and cost function
  % penalty I used. Seems unnecessary since it is all in my code.
  %MRS4: I would put in supporting.

@@

  %MRS2: Be more explicit than 'instructive'' - ``Where it help to demonstrate X'' or something like that?
  Where instructive, we differentiated between the length of hops inside
  and outside of the pores. For 10 wt\% water systems, we consider a solute
  to be in the pore if it is within 0.75 nm of a pore center. This radial
  cut-off maximizes the difference between average hop lengths in and out
  of the pore. See Section~\ref{S-section:pore-region} of the Supporting
  Information for further details on this optimization.

@@

  We measured the average radial distance of each solute of interest 
  from the pore centers. We binned the radial distances and then 
  normalized by the volume of the annulus defined by the bin edges.
  We generated 1$\sigma$ confidence intervals by bootstrapping the 
  RDFs of each individual solute 200 times. For each solute, we obtained
  an RDF averaged over the entire simulation trajectory. We randomly 
  %MRS2: tweaked for clarity
  chose individual solute RDFs with replacement from the set of 24 and averaged 
  each set for each bootstrap
  trial in order to generate a distribution from which to calculate uncertainties. 
  This approach assumes that solute positions are uncorrelated to
  other solutes which we believe is valid due to the low degree of 
  interaction between solutes described in Section~\ref{method:system_setup}.

@@

  In contrast to our previous work with a dry version of this membrane, the 
  region close to the pore center of the 5 and 10 wt\% water systems is 
  primarily filled with water and sodium ions. Figure~\ref{fig:component_densities}
  plots the RDF of each membrane constituent in the dry system as well as the
  5 and 10 wt\% water systems. In dry systems, the pore center is densely 
  filled with sodium ions and head groups. In hydrated systems, water occupies, 
  and is densest, at the center of each pore. The density of sodium ions is 
  somewhat uniform in the pore center of the 5 wt\% water system while it shows
  a maximum closer to the head groups in the 10 wt\% water system. The peak 
  density of sodium ions is not at the pore center in the 10 wt\% water system
  likely because they are 
  %MRS2: not that loose
  %still loosely 
  associated with the monomer's carboxylate
  head groups.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_dry.pdf}  % running this out on bridges to make smoother
  %BJC: simulation is extended to smooth out these curves
  \caption{Dry System}\label{fig:component_density_dry}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
  \label{fig:monomer_color_coded}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  %MRS2: interesting that the head group max is near the transition point where water/tail groups 
  \caption{The radial densities of various monomer components paint a 
  picture of the pore topology where the pore centers of hydrated systems are primarily,
  but not exclusively, composed of water and sodium ions. The monomer groups labeled in each plot correspond to 
  the color-coded monomer pictured in the upper right corner of the figure. 
  RDFs show the average number of atoms located at a given distance from the
  pore center normalized by the volume of the annular bin to which they belong.
  The vertical dashed black lines are positioned so that they intersect with 
  the maximum head group density.
  (a) In the dry system, the density of head groups and sodium ions are highest
  0.15 to 0.4 nm from the pore center. There is an appreciable density of head groups
  crowding the pore center. (b) In the 5 wt\% system, monomer head 
  groups retreat radially in order to make room for water molecules at the pore center.
  (c) Monomers in the 10 wt\% system retreat an additional 0.2 nm to make room
  for more water.}\label{fig:component_densities}
  %MRS4: dotted horizontal line not defined.
  \end{figure}

@@

  There is an appreciable amount of water that partitions into the distal tail % BJC: defined in methods
  region of both systems. 28\% and 31\% of the total water is present in the
  distal tail regions of the 5 and 10 wt\% water systems respectively. See 
  Section~\ref{S-section:water_content_equil} of the Supporting Information 
  for more details on the equilibration that led to this conclusion. The partition
  is due to a combination of the distal tail region's lower density as well
  as oxygen atoms at the ends of each monomer tail which can further stabilize
  water molecules. See Figure~\ref{S-fig:total_density} of the Supporting 
  Information for a graphical illustration of this point.

@@

  %MRS2: changed tense to present on the paper itself, past on studies leading to the paper.
  We observed transport of sodium, water and 20 other small polar solutes
  inside the membrane nanopores. First, we comment on transport of the
  membrane constituents, water and sodium, in a system absent of any additional
  solutes. We then present the general trends that we observe among the
  all other solutes studied.

@@

  % Changing pore radius does not change conclusion here.
  In the 5 wt\% water system, water molecules that spend the majority of their 
  time in the distal tail region have MSDs higher than those of water molecules
  close to the pore center. The MSD of distal tail water molecules is 1.7 nm$^2$
  compared to 1.2 nm$^2$ outside the distal tails. This anomaly is likely a 
  consequence of lower density in the distal tails relative to the pores,
  leading to faster diffusion in the tails,
  as well as slowed diffusion of water molecules in the pores via hydrogen bonds
  with other water molecules and association with sodium ions. Water molecules 
  are less likely to hydrogen bond with each other while in the distal tail 
  region since they are interspersed between chains, while those in 
  the pores stay in close proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
  %MRS4: but there is also H-bonding to ions and carboxylate groups, which seems like they should be even stronger than water-water.
  hydrogen bonding between water molecules near the pore center versus those in 
  the distal tail region. Additionally, an average of 65\% of water molecules in
  the pores of the 5 wt\% water system are associated with a sodium ion each frame
  compared to 44 \% in the 10 wt\% water system. There is a negligible amount of
  hydrogen bonds between water molecules and monomer head groups.

  %MRS2: some tweaking
  Because the MSD of water in the pores of the 10 wt\% system is significantly
  higher than that in the tails, we restrict our studies of transport in this paper to 
  solutes in or near the pore center. Transport of solutes in the pores will be the 
  limiting factor that determines permeability and rejection. Although tail transport of water in the 
  the 5 wt\% water system is faster than pore transport, water transport overall is significantly slower
  than in the 10 wt\% system. For practical applications, a membrane with water 
  transport properties comparable to the 10 wt\% system is far more feasible than
  the 5 wt\% system.

@@

  %MRS2: tweak
  %Like water and sodium above, 
  As with water and sodium,
  the MSDs of the solutes studied in this work are 
  significantly larger in the 10 wt\% system than those in the 5 wt\% water 
  system (see Figures~\ref{fig:all_msds_5wt} and~\ref{fig:all_msds_10wt}). The fastest moving solute in both cases, 
  methanol, has an MSD about 175 times larger in the 10 versus the 5 wt\%
  water system. Clearly the equilibrium water content of a given LLC system will 
  determine its viability for real separations.

>>>>

  The uniform size and complex chemical topology of the pores that 
  constitute cross-linked inverted hexagonal (H\textsubscript{II})
  phase lyotropic liquid crystal (LLC) membranes make them promising
  for selective separations. In this work, we observe transport
  of water, sodium ions and 20 small polar solutes within the pores 
  of an LLC membrane using atomistic molecular simulations. We 
  find that the transport of a species is dependent not only on 
  molecular size, but on chemical functionality as well. The 
  membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. We observe
  that all solutes perform intermittent hops between lengthy
  periods of entrapment. Three different trapping mechanisms are 
  responsible for this behavior. First, solutes that drift
  out of the pore can become entangled among the dense monomer
  tails. Second, solutes can donate hydrogen bonds to the monomer
  head groups. Third, solutes can coordinate with sodium counter ions.
  The degree to which a solute is affected by each mechanism is 
  dependent on the chemical functionality of the solute. Using the
  insights developed in this study, we can begin to think about 
  how to redesign existing LLC membranes in order to perform 
  solute-specific separations.

@@

  All of these separations are possible in part with current commercial
  membrane separation techniques, but all still suffer from serious drawbacks.
  Currently, reverse osmosis (RO) and nanofiltration (NF) dominate commercial membrane
  separations of small molecules.~\cite{warsinger_review_2018} RO membranes are
  typically dense polymer matrices that separate solutes based on differences in
  their solubility and permeability in the membrane
  material.~\cite{fritzmann_state---art_2007} Although they can perform highly
  selective separations, high feed pressures and thus large amounts of energy
  are necessary in order to generate a useful permeate
  flux.~\cite{van_der_bruggen_review_2003} NF membranes have well-defined
  nm-sized pores which can give the same permeate flux as RO with lower applied
  pressure.~\cite{hilal_comprehensive_2004} However, the pores are not uniform in
  size, limiting their selectivity.~\cite{werber_materials_2016}.
%  Therefore, multiple membrane passes may be necessary in order to achieve 
%  high selectivity.

@@

  In this work, we present studies of the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of
  the membrane in which we placed solutes. We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
  Note that, in order limit our studies to uncharged species, we have only studied
  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
  pKa of acetic acid is 4.75.~\cite{chuysinuan_gallic_2009,perrin_pka_1981} 
  Assuming that the pKa of gallic acid is similar to NaGA3C11, it is possible
  for our sodium salted monomer to exist at the same time as protonated acetic
  acid. In any case, we are more interested in mechanisms of interaction with
  specific chemical functionality more than the behavior of specific molecules.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ortho_view.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{top_view.pdf}
  \caption{}
  \end{subfigure}
  %MRS3: include a bit more description in the caption of what the system: This is the figure that provides the orientation to the readers of what they will be thinking about for the rest of the paper.
  %BJC3: gave it another shot
  \caption{The H\textsubscript{II} phase formed by LLC monomers consists of pores
  that are approximately straight (a) and packed hexagonally (b). In both figures,
  water molecules that occupy the pores are colored blue, the hydrophilic head 
  groups of the LLC monomers are colored orange and all else is colored gray. 
  The chemical environment within the nanopores is largely determined by the functionality
  of the head groups. Additionally, there is not a well-defined transition
  point from the aqueous pore region to the alkane-dense, hydrophobic tail region,
  generating further complexity.
  }\label{fig:membrane_rendering}
  \end{figure}

  \begin{table}[h!]
  \centering
  \begin{tabular}{ |m{3.5cm}m{1.4cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
    \hline
    \multicolumn{2}{|c}{Solute Name~~~~~~~~~Abbreviation} & Structure &\multicolumn{2}{c}{Solute Name~~~~~~~~~Abbreviation} & Structure \\
    \hline
	\color{blue}{\textbf{methanol}} & \color{blue}{\textbf{MeOH}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/MET.pdf}
    \end{minipage} &

@@

    \hline
  \end{tabular}
  \caption{Names of solutes along with their molecular structures and the
  abbreviations which we use in this paper. Colors correspond to solute groupings
  and are used in many plots. 
%  Blue corresponds to simple alcohols, red to 
%  diols, triols and sugars, green to ketone-like solutes, orange to sulfur-containing
%  solutes and yellow to solutes that can only accept hydrogen bonds but not donate.
  }\label{table:abbreviations}
  \end{table}

  %MRS2: generally, use present tense for what is being done in the paper, not future tense; 
  %the paper is completely written, later sections are not being written in the future. 
  %MRS2: descriptions of experiments can be in the past.   
  %MRS2: look over this section at the end of the intro again for clarity - some paragraphs are too short (ideas introduced and brushed past quickly) sometimes without strong theses.
  %BJC3: I think these make more sense now.

  We first address the structure of the membrane nanopores. Previously, we
  studied dry membrane systems and some systems with low water content. We showed
  that those systems have rather crowded pores with high concentrations of monomer
  head groups, sodium ions and water, where applicable. Here we build systems with
  appreciable amounts of water, 5 and 10\% by weight, and analyze how the radial
  density of monomer components and water change compared to our previous results.

%  We then present our efforts to understand how water partitions within the pores.  
  We then use the transport rates of water in and out of the pores in order to
  to justify our study of solute transport restricted to the pore region. From a 
  macroscopic perspective, it might make sense to hypothesize that water spends its time 
  exclusively in the tube-like hydrophilic pore region. Our previous work showed
  that there is a gradual compositional transition from the hydrophilic to the
  hydrophobic region which means that solutes may not necessarily stay confined
  to the centers of the pores or even within the pore region. We show that, in 
  our most viable system, water moves fastest within the pores suggesting that 
  the pores should be the focus of our mechanistic studies.

  %MRS2: ``this information'' is ambiguous. Which information? Also, I'm not sure the paragraph above is enough to 
  %demonstrate why we can/should neglect the tails.
%  We use this information in order to justify our restriction
%  of solute transport studies to just the pore region.

@@

  In the remainder of the paper, we describe and quantify three trapping 
  mechanisms which give rise to subdiffusive solute transport behavior. 
  We investigated the differences in solute motion, specifically their mean
  squared displacement (MSD), in conjunction with each solute's size and 
  chemical functionality. We show how distinct interactions with various
  monomer components as well as membrane water content hinders the motion 
  of solutes. We discuss how the interactions between specific solutes and
  the membrane depend on the solute's chemical functionality.
%    We present the interactions between solutes, the membrane,
%  and water in order to determine which mechanism or mechanisms dominate.
%  present our observations and explanations 
%  of the observed transport mechanisms exhibited by water and solutes. 
  %MRS2: The thesis of this paragraph could be stronger. expand ``pores will restrict motion of the solutes'' a little using the physical details about the pores; paint the picture that will be filled in with detail   
  %BJC3: redone above.
%  Given that the pores will restrict motion of the solutes, we
%  anticipate that transport will be hindered in some way.

  There are also several questions beyond the scope of this study.
  First, we will not study the concentration dependence of the observed transport
  rates. Although the average MSD might change with concentration, we are 
  focused on the underlying solute-membrane interactions that lead to the 
  observed transport mechanisms which we conjecture will remain roughly
  the same regardless of concentration. Second, we will not study the chemical potential
  of solutes in the pores, which could give us a better understanding of 
  equilibrium solute partitioning. However, this information is likely
  not needed to understand the principal mechanistic details in various membrane
  regions. This work instead represents a starting point for observing the 
  types of interactions that occur between isolated solutes and the membrane.

@@

  Python scripts used to set up systems and conduct post-simulation trajectory 
  analysis (as described below and in the supporting information) are available 
  online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. The 
  appropriate scripts to use for the subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supporting Information. We ran all 
  MD simulations and energy minimizations using GROMACS 2018.3.~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}

@@

  We observed that some water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
  Information). We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent; otherwise, water would slowly leak from the pore into the
  tail region over several hundred nanoseconds. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region. We 
  justify this decision with better context in Section~\ref{section:transport_water_sodium}.
  %MRS2: seems like here is where we need to provide the justification for this decision, since the decision is described here (or, explain how we will justify it later)
  %BJC3: added reference to later section.

@@

  The $z$-direction MSD of water in the 10 wt\% system \textit{is} linear to within 
  statistical precision. Therefore, for the purpose of comparison, we calculated its
  %BJC3: linear within statistical precision --> appears linear? I didn't do any rigorous tests for linearity
  diffusion constant by fitting a line to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured particle displacement in one dimension.

@@

  In order to measure the length of hops, we first needed to detect
  when they occurred. We used an off-line change point detection 
  algorithm, implemented in the python package \texttt{ruptures}
  \cite{truong_ruptures:_2018}, in order to determine at which 
  points hops occurred in the time series of each solutes' COM. We
  used the 3 dimensional COM positions of each solute, rather than
  just the $z$-direction, in order to detect lateral hops. However,
  hop lengths are reported as their displacement in the $z$-direction.
  We reported the standard error in the average hop lengths by 
  bootstrapping the empirical distribution of observed
  hop lengths.\cite{efron_introduction_1994}

@@

  We differentiated between the length of hops inside and outside of the 
  pores. For 10 wt\% water systems, we consider a solute to be in the pore
  if it is within 0.75 nm of a pore center. This radial cut-off maximizes 
  the difference between average hop lengths in and out of the pore. 
  See Section~\ref{S-section:pore-region} of the Supporting
  Information for further details on this optimization.

@@

  We measured the average radial distance of each solute of interest 
  from the pore centers. We binned the radial distances and then 
  normalized by the volume of the annulus defined by the bin edges.
  We generated 1$\sigma$ confidence intervals by bootstrapping the 
  RDFs of each individual solute 200 times. For each solute, we obtained
  an RDF averaged over the entire simulation trajectory. We randomly 
  chose individual solute RDFs with replacement from the set of 24 and averaged 
  each set for each bootstrap trial in order to generate a distribution from 
  which to calculate uncertainties. 
  This approach assumes that solute positions are uncorrelated to
  other solutes which we believe is valid due to the low degree of 
  interaction between solutes described in Section~\ref{method:system_setup}.

@@

  In contrast to our previous work with a dry version of this membrane, the 
  region close to the pore center of the 5 and 10 wt\% water systems is 
  primarily filled with water and sodium ions. Figure~\ref{fig:component_densities}
  plots the RDF of each membrane constituent in the dry system as well as the
  5 and 10 wt\% water systems. In dry systems, the pore center is densely 
  filled with sodium ions and head groups. In hydrated systems, water occupies, 
  and is densest, at the center of each pore. The density of sodium ions is 
  somewhat uniform in the pore center of the 5 wt\% water system while it shows
  a maximum closer to the head groups in the 10 wt\% water system. The peak 
  density of sodium ions is not at the pore center in the 10 wt\% water system
  likely because they are associated with the monomer's carboxylate head groups.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_dry.pdf}  % running this out on bridges to make smoother
  %BJC: simulation is extended to smooth out these curves
  %BJC3: update: got slightly smoother
  \caption{Dry System}\label{fig:component_density_dry}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
  \label{fig:monomer_color_coded}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  %MRS2: interesting that the head group max is near the transition point where water/tail groups 
  \caption{The radial densities of various monomer components paint a 
  picture of the pore topology where the pore centers of hydrated systems are primarily,
  but not exclusively, composed of water and sodium ions. The monomer groups labeled in each plot correspond to 
  the color-coded monomer pictured in the upper right corner of the figure. 
  RDFs show the average number of atoms located at a given distance from the
  pore center normalized by the volume of the annular bin to which they belong.
  The vertical dashed black lines are positioned so that they intersect with 
  the maximum head group density.
  (a) In the dry system, the density of head groups and sodium ions are highest
  0.15 to 0.4 nm from the pore center. There is an appreciable density of head groups
  crowding the pore center. (b) In the 5 wt\% system, monomer head 
  groups retreat radially in order to make room for water molecules at the pore center.
  (c) Monomers in the 10 wt\% system retreat an additional 0.2 nm to make room
  for more water.}\label{fig:component_densities}
  \end{figure}

@@

  There is an appreciable amount of water that partitions into the distal tail
  region of both systems. 28\% and 31\% of the total water is present in the
  distal tail regions of the 5 and 10 wt\% water systems respectively. See 
  Section~\ref{S-section:water_content_equil} of the Supporting Information 
  for more details on the equilibrations that led to this conclusion. The partition
  is due to a combination of the distal tail region's lower density as well
  as oxygen atoms at the ends of each monomer tail which can further stabilize
  water molecules. See Figure~\ref{S-fig:total_density} of the Supporting 
  Information for a graphical illustration of this point.

  We will restrict our studies of transport to solutes and water outside of the 
  distal tail region because transport is fastest in the pores. We provide more 
  rigorous justification for this restriction at the end of Section~\ref{section:transport_water_sodium}.

@@

  We observed transport of sodium, water and 20 other small polar solutes
  inside the membrane nanopores. First, we comment on transport of the
  membrane constituents, water and sodium, in a system absent of any additional
  solutes. We then present the general trends that we observe among the
  all other solutes studied.

@@

  % Changing pore radius does not change conclusion here.
  In the 5 wt\% water system, water molecules that spend the majority of their 
  time in the distal tail region have MSDs slightly higher than those of water molecules
  close to the pore center. The MSD of distal tail water molecules is 1.7 nm$^2$
  compared to 1.2 nm$^2$ outside the distal tails. This anomaly is likely a 
  consequence of lower density in the distal tails relative to the pores,
  leading to faster diffusion in the tails,
  as well as slowed diffusion of water molecules in the pores via hydrogen bonds
  with other water molecules and association with sodium ions. Water molecules 
  are less likely to hydrogen bond with each other while in the distal tail 
  region since they are interspersed between chains, while those in 
  the pores stay in close proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
  hydrogen bonding between water molecules near the pore center versus those in 
  the distal tail region. Additionally, an average of 65\% of water molecules in
  the pores of the 5 wt\% water system are associated with a sodium ion each frame
  compared to 44 \% in the 10 wt\% water system. There is a negligible amount of
  hydrogen bonds between water molecules and monomer head groups.

  Because the MSD of water in the pores of the 10 wt\% system is significantly
  higher than that in the tails, we restrict our studies of transport in this paper to 
  solutes in or near the pore center. Transport of solutes in the pores will be the 
  limiting factor that determines permeability and rejection. Although tail transport of water in the 
  the 5 wt\% water system is faster than pore transport, water transport overall is significantly slower
  than in the 10 wt\% system. For practical applications, a membrane with water 
  transport properties comparable to the 10 wt\% system is far more feasible than
  the 5 wt\% system.

@@

  As with water and sodium, the MSDs of the solutes studied in this work are 
  significantly larger in the 10 wt\% system than those in the 5 wt\% water 
  system (see Figures~\ref{fig:all_msds_5wt} and~\ref{fig:all_msds_10wt}). The fastest moving solute in both cases, 
  methanol, has an MSD about 175 times larger in the 10 versus the 5 wt\%
  water system. Clearly the equilibrium water content of a given LLC system will 
  determine its viability for real separations.
